Estimating Output Loss due to being Unrecognized as States

### 2019-02-28 paper/paper.tex
Use the logarithm, not the level, of GDP and light #1 #28 #30
Draft the results section #41

\section{Methodology}
% Model of real GDP
We model real GDP in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdp}
y_{it} = \beta L_{it} + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.

@@

% Model of country fixed effects
To predict $y_{it}$ for unrecognized states (and their parent countries dropped from the sample) from equation (\ref{gdp}), we need to recover territory fixed effects, $\mu_i$. 
We predict them with the average light intensity over the sample period of 1992-2013. 
Specifically, with the same set of countries as the one for estimating equation (\ref{gdp}), we estimate the following equation with OLS:
\begin{equation}\label{country_fe}
\hat{\mu}_i = \alpha + \gamma \bar{L}_{i} + \xi_{i},
\end{equation}
where $\hat{\mu}_i$ is the estimated territory fixed effect from equation (\ref{gdp}), $\bar{L}_{i}$ the average light intensity in territory $i$ over the sample period, and $\xi_i$ the error term.

% Prediction of real GDP
Consequently, GDP per capita in unrecognized state $k$ in year $t$, denoted by $\hat{y}_{kt}$, will then be predicted as follows:
\begin{equation}
\hat{y}_{kt} = \hat{\beta} L_{kt} + [\hat{\alpha} + \hat{\gamma} \bar{L}_{i}]  + \hat{\eta_t},
\end{equation}
where $\hat{\beta}$ and $\hat{\eta_t}$ are the estimated $\beta$ and $\eta_t$ in equation (\ref{gdp}), $\hat{\alpha}$ and $\hat{\gamma}$ the estimated $\alpha$ and $\gamma$ in equation (\ref{country_fe}).

\section{Results}
\section{Conclusions}

>>>>

\section{Methodology}
% Model of real GDP
We model real GDP in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdp}
\ln(y_{it}) = \beta \ln(L_{it}) + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.

@@

% Model of country fixed effects
To predict $y_{it}$ for unrecognized states (and their parent countries dropped from the sample) from equation (\ref{gdp}), we need to recover territory fixed effects, $\mu_i$. 
We predict them with the average light intensity over the sample period of 1992-2013. 
Specifically, with the same set of countries as the one for estimating equation (\ref{gdp}), we estimate the following equation with OLS:
\begin{equation}\label{country_fe}
\hat{\mu}_i = \alpha + \gamma \ln(\bar{L}_{i}) + \xi_{i},
\end{equation}
where $\hat{\mu}_i$ is the estimated territory fixed effect from equation (\ref{gdp}), $\bar{L}_{i}$ the average light intensity in territory $i$ over the sample period, and $\xi_i$ the error term.

% Prediction of real GDP
Consequently, GDP per capita in unrecognized state $k$ in year $t$, denoted by $\hat{y}_{kt}$, will then be predicted as follows:
\begin{equation}\label{prediction}
\ln(\hat{y}_{kt}) = \hat{\beta} \ln(L_{kt}) + [\hat{\alpha} + \hat{\gamma} \ln(\bar{L}_{i})]  + \hat{\eta_t},
\end{equation}
where $\hat{\beta}$ and $\hat{\eta_t}$ are the estimated $\beta$ and $\eta_t$ in equation (\ref{gdp}), $\hat{\alpha}$ and $\hat{\gamma}$ the estimated $\alpha$ and $\gamma$ in equation (\ref{country_fe}).

\section{Results}
The results from estimating equation (\ref{gdp}) are reported in Table \ref{panel_results}. 
The elasticity of real GDP with respect to nighttime light intensity is xxx (significant at the x\% level). 
Year fixed effect estimates are also reported as these values will be used to predict real GDP for unrecognized states.

Table \ref{country_fe_results} reports the results from estimating equation (\ref{country_fe}). 
The country fixed effects estimated from equation (\ref{gdp})) are proportional to the average light intensity. 
Figure \ref{country_fe_graph} plots the country fixed effects against the average light intensity.

Plugging the coefficient estimates in Tables \ref{panel_results} and \ref{country_fe_results} as well as annual nighttime light observations into equation (\ref{prediction}) yields the predicted real GDP for unrecognized states and their parent countries. 
We plot these predicted values over time in Figure \ref{predicted_gdp}. 
As a validation exercise, we also plot the observed annual real GDP for the respective parent country, obtained from the Penn World Table.

\section{Conclusions}
